Curiosity-Driven Development of Tool Use Precursors: a Robotic Model

### 2016-01-29 cogsci2016/paper.tex
discussion

			A first condition is to randomly choose the model that will find a goal, this is Random Model Babbling (H-RGB-RMB).
			The problem of Model Babbling is an instance of strategic learning \cite{nguyen2012}, 
			where different outcomes and strategies to learn them are available and the agent learns which strategies are useful for which outcomes.
			In that paper, they show that an active choice of the outcomes and strategies based on the learning progress on each of them increase learning efficiency compared to random choice.
			To develop active learning strategies, we first define a measure of learning progress for each of the $6$ models.
			When a model has been chosen to babble, it draws a random goal $s_g$, and finds motor parameters $m$ to reach it using the lower-level models.
			The actual outcome $s$ in the sensory space of the model, associated to $m$ might be very different from $s_g$ as this goal might be unreachable, or because lower-level models are not mature enough for that goal.
			We define the competence associated to a goal $s_g$ as $C(s_g)=-||s_g-s||$, and the interest $I(s_g)$ associated to this goal
			as the absolute difference between $C(s_g)$ and the mean competence of the ($k=20$) nearest previous goals.
			The interest of a model is initialized at $0$ and updated to follow the interest of the goals:
			\begin{equation}
				I_{model}=\frac{n-1}{n}~I_{model} + \frac{1}{n}~I(s_g)
			\end{equation}
			In condition H-RGB-P-AMB, the choice of model is proportional to their interest (probabilities are proportional to interest but with $\epsilon=10\%$ of random choice). 
			In condition H-RGB-GR-AMB, the choice of model is greedy (model with maximum interest) but also with $\epsilon=10\%$ of random choice.
			Finally, condition H-RGB-P-AMB-PGITC is the same as H-RGB-P-AMB but the choice of the tool to use (model $3$ or $6$) is with probabilities proportional to the interest of the two models, 
			instead of being based on the more competent tool for the given object goal position.

@@

	\subsection{F-RGB vs H-RGB-P-AMB vs H-RGB-GR-AMB}

		Results show different structures of behavior evolution in those 3 conditions.

		Results show that random model babbling and active model babbling both show overlapping waves structure in the evolution of the three behaviors, 
		but random model babbling explores slightly less the object position.
		In this setup, the difference is more on the cognitive or intentional level, as active model babbling monitors the progress on each model whereas random model babbling do not, than on a quantitative level, 
		because here all models are still useful to explore.
		However, in others setups where some tasks are learned much faster than others and where at some point it become useless to explore a mastered task, then active model babbling would
		make a key difference on a quantitative exploration point of view, and on the structure of the evolution of the measured behaviors.

@@

	\subsection{H-RGB-P-AMB vs H-RGB-P-AMB-PGITC}

>>>>

			A first condition is to randomly choose the model that will find a goal, this is Random Model Babbling (H-RGB-RMB).
			The problem of Model Babbling is an instance of strategic learning \cite{nguyen2012}, 
			where different outcomes and strategies to learn them are available and the agent learns which strategies are useful for which outcomes.
			In that paper, they show that an active choice of the outcomes and strategies based on the learning progress on each of them increase learning efficiency compared to random choice.
			To develop active learning strategies, we first define a measure of learning progress for each of the $6$ models.
			When a model has been chosen to babble, it draws a random goal $s_g$, and finds motor parameters $m$ to reach it using the lower-level models.
			The actual outcome $s$ in the sensory space of the model, associated to $m$ might be very different from $s_g$ as this goal might be unreachable, or because lower-level models are not mature enough for that goal.
			We define the competence associated to a goal $s_g$ as minus the distance between the goal and the reached point, divided by the maximal distance in this space, to scale this measure across different spaces:

			\begin{equation}
				C(s_g)=-\frac{||s_g-s||}{max_{s'}||s'-s||}
			\end{equation}
			 and the interest $I(s_g)$ associated to this goal as 
			\begin{equation}
				I(s_g) = |C(s_g) - mean_{kNN}C(s)|
			\end{equation}
			the absolute difference between $C(s_g)$ and the mean competence of the ($k=20$) nearest previous goals.
			The interest of a model is initialized at $0$ and updated to follow the interest of the goals (with rate $n=200$):
			\begin{equation}
				I_{model}=\frac{n-1}{n}~I_{model} + \frac{1}{n}~I(s_g)
			\end{equation}
			In condition H-RGB-P-AMB, the choice of model is proportional to their interest (probabilities are proportional to interest but with $\epsilon=10\%$ of random choice). 
			In condition H-RGB-GR-AMB, the choice of model is greedy (model with maximum interest) but also with $\epsilon=10\%$ of random choice.
			Finally, condition H-RGB-P-AMB-PGITC is the same as H-RGB-P-AMB but the choice of the tool to use (model $3$ or $6$) is with probabilities proportional to the interest of the two models, 
			instead of being based on the more competent tool for the given object goal position.

@@

	\subsection{Structure of the evolution of behavior}

		Results show different structures of behavior evolution in the different conditions.
		F-RGB shows 
		H-RGB-GR-AMB shows successive behavioral steps with abrupt changes.
		Random model babbling and active model babbling both show overlapping waves structure in the evolution of the three behaviors, 
		but random model babbling explores slightly less the object position.
		In this setup, the difference is more on the cognitive or intentional level, as active model babbling monitors the progress on each model whereas random model babbling do not, than on a quantitative level, 
		because here all models are still useful to explore.
		However, in others setups where some tasks are learned much faster than others and where at some point it become useless to explore a mastered task, then active model babbling would
		make a key difference on a quantitative exploration point of view, and on the structure of the evolution of the measured behaviors.

@@

	\subsection{Variability of strategies to reach goals}
